Make any stupid plot you want

### 2021-01-04 draft/sections/math.tex
math

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \label{tab:mpl_visual_variable_fiber}
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, colors, linecolor, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^4$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $(\mathbb{N}, \mathbb{N}^{n})$ \\ \hline              
    \end{tabulary}
\end{table}

\subsubsection{Visual Channels}
$\nu: \tau \mapsto \mu$ is an equivariant map such that there is a homomorphism from monoid actions on $E_{i}$ to manoid actions on $V_{i}$  
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "f"'] & V_i \arrow[d, "f"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
where the diagram commutes such that  $\nu g(\tau_{i}) = g(\nu(tau_{i})$. Monoid actions are:
1) set of functions including identity, composition operator, closed, associative

To construct a valid $\nu$:
\begin{enumerate}
    \item identify monoid actions on $E_i$
    \item choose $V_i$ that can support same monoid actions
    \item implement $\nu$ such that composition holds
\end{enumerate}

\paragraph{Example: Translation}
When $tau_{i}$ of $E_1$ returns interval data, Steven's defines the group actions on the data as the general linear group \cite{stevensTheoryScalesMeasurement1946,leaFormalizationMeasurementScale}; therefore to construct a valid $\nu$, we choose a target variable in $P$ that is

@@

\paragraph{Example: Partial Order}
$\nu$ induces a monoid homomorphism, rather than a group homomorphism, to allow for partial ordering. For example if E1 is the set '{}

@@

\end{document}

>>>>

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \label{tab:mpl_visual_variable_fiber}
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, linecolor, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $(\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
\end{table}

\subsubsection{Visual Channels}
$\nu: \tau \mapsto \mu$ is an equivariant map such that there is a homomorphism from monoid actions on $E_{i}$ to manoid actions on $V_{i}$  
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "f"'] & V_i \arrow[d, "f"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
where the diagram commutes such that  $\nu_{i}\circ f(\tau_{i}) = f \circ \nu_{i}(\tau_{i})$. A monoid is a set $M$ with a closed associative binary operation ($\*$) and an identity element $e$.

\paragraph{Example: Translation}
When $\tau_{i}$ of $E_1$ returns interval data, Steven's defines the group actions on the data as the general linear group \cite{stevensTheoryScalesMeasurement1946,leaFormalizationMeasurementScale}; therefore to construct a valid $\nu$, we choose a target variable in $P$ that is

@@

\paragraph{Example: Partial Order}
$\nu$ induces a monoid homomorphism to allow for partial ordering. For example if E1 is the set '{}

@@

Bertin describes a location on the plane as the signifying characteristic of a point, measurable length as the signifying characteristic of a line, and measurable size as the signifying characteristic of an area and that in display (pixel) space are the point, line, and area marks \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology}. For each region $s$ in the display space $H$, the mark it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$ then taking $\xi(s)$ back to a point on $k \in K$ which lies on the connected component $J \subset K$. 
\begin{equation}
\begin{tikzcd}
    H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K| \exists \Gamma \text{ s.t. } \Gamma(0)=k \text{ and }\Gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
\end{tikzcd}
\label{eq:mark}
\end{equation}
To got back to the display space $H$  from the simplacial complex $J$ of the signifier implanted in the mark, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then  $\rho(\xi^{-1}(J))$ maps it into $R^{7}$.

\subsubsection{Visual Idioms: Equivalance class of artists}
n $O(E)$ of the same type, they output the same type of prerender $O(H)$:

Natural transformation + composition is partial ordering? Back and forth is equivalent 
\end{document}
